Altering Backward Pass Gradients improves Convergence

### 2022-09-19 paper.tex
Mod9

% \usepackage{xcolor}
% \usepackage{pagecolor}
% \pagecolor{black}
% \color{white}

@@

\begin{figure}[!t]
\centering
\begin{subfigure}{.33\textwidth}
\centering
\includegraphics[width=0.98\textwidth]{acc_vs_epoch_r18}
\caption{Plot of training and test accuracies (ResNet-18)}
\end{subfigure}%
\begin{subfigure}{.33\textwidth}
\centering
\includegraphics[width=0.98\textwidth]{acc_vs_epoch_r50}
\caption{Plot of training and test accuracies (ResNet-50)}
\end{subfigure}%
\begin{subfigure}{.33\textwidth}
\centering
\includegraphics[width=0.98\textwidth]{acc_vs_epoch_r50_60epochs}
\caption{Plot of test accuracies (ResNet-50)}
\end{subfigure}
\caption{ Log-linear plots of training and test accuracies and comparison with baseline
of batch-normalized variants: \textbf{(a)} ResNet-18 ($\alpha=0.25$), \textbf{(b)}
ResNet-50 ($\alpha=0.3$). For better visualization of accuracies obtained in the final
iterations, we plot both axes in log scale. PowerGrad Transform improves upon the
baseline in all cases. The corresponding accuracies are mentioned in table
\ref{tab:imagenet_table}. \textbf{(c)} Training speed comparison between PGT ($60$
epochs) and baseline ($100$ epochs). They both converge to the same test accuracy
($76.5\%$) on ImageNet-1K. PGT's accelerated training saves $40\%$ of the epoch budget.
}
\label{fig:metrics}
\end{figure}

@@

We perform experiments on different variants ResNets using the ImageNet-1K dataset
\cite{deng2009imagenet}. All models are trained on four V100 GPUs with a batch size of
$1024$. We utilize a common set of hyperparameters for all experiments, which are as
follows: 100 epoch budget, 5 epochs linear warmup phase beginning with a learning rate
of $4\times 10^{-4}$ and ending with a peak learning rate of $0.4$, a momentum of $0.9$
and weight decay of $5\times 10^{-4}$, the SGD Nesterov optimizer and mixed precision.
In our studies, we employ either a step scheduler (dividing the learning rate by $10$ at
the $30^{th}$, $60^{th}$, and $90^{th}$ epochs) or a cosine decay scheduler
\cite{loshchilov2016sgdr}. We find $\alpha=0.25$ and $\alpha=0.05$ to be good choices
for ResNet-18 and ResNet-50, though larger values such as $\alpha=0.3$ also have good
performance as well. The experimental results are shown in table
\ref{tab:imagenet_table}, and we mention the value of the PGT hyperparmeter ($\alpha$)
in each experiment. We explore different values of $\alpha$ in section \ref{sec:Abla}
and provide detailed grid plots in the supplementary section.

In our experiments with Squeeze-and-Excitation variant of ResNet-50 i.e.
SE-ResNet-50\cite{hu2018squeeze}, we observe significant improvements; a $0.97\%$ boost
in training accuracy and a $0.734\%$ increase in test accuracy. Therefore, PGT also
speeds up training. In our experiments with ResNet-50, we find an increase of $0.5\%$
and $0.656\%$ performance enhancement over the baseline while using the cosine
scheduler. The corresponding improvement over the step scheduler baseline for ResNet-50
is $0.57\%$ and $0.524\%$ respectively for training and testing. ResNet-101 sees a
higher improvement in training fit, $0.81\%$ to be exact, while the improvement over the
test set is $0.362\%$. Smaller networks such as SE-ResNet-18 and ResNet-18 sees accuracy
boosts which are smaller but nevertheless positive. Therefore we conclude that with PGT,
the consistent improvements in training accuracies across all cases is because the
networks train better and arrive at better optimas during convergence. Per epoch
training and test accuracy plots of ResNet-18 and ResNet-50 (both with and without PGT)
are shown in Fig. \ref{fig:metrics}(a, b). For better visualization of the top end of
the plots, we scale both axes in log scale. Our experiments with batch-normalized
networks indicate that PowerGrad Transform speeds up training and allows the network to
learn better representations\footnote{Reproducible code, training recipes for the
experiments, pretrained checkpoints and training logs are provided at: \\
\url{ https://github.com/bishshoy/power-grad-transform }. Code is adapted from
\cite{rw2019timm}.}.

These improvements are obtained with the number of epochs being kept the same as that of
the baseline model. Alternatively, practitioners can apply PGT and have the networks
converge to accuracy levels comparable to the baseline with a significantly reduced
epoch budget. In Fig. \ref{fig:metrics}(c), we illustrate one such instance in which we
train a ResNet-50 to its cosine scheduler baseline in just $60$ epochs with PGT, and
match its baseline performance that is acquired in $100$ epochs. Because of the
acceleration in training that is made possible by PGT, the total amount of training time
can be decreased by $40\%$.

@@

AGC is excellent at eliminating the issue of filter and feature zeroing out. However,
AGC recovers a lower performance benefit than PGT. In the instance of PGT, we see that
it also mitigates the zeroing out phenomenon in most layers. In
Fig.\ref{fig:agc_pgt}(a), we see a plot of the $15^\textit{th}$ layer of the non-BN
ResNet-18 trained without PGT. As we can see that there has been quite a few filter
dropouts in the baseline. PGT recovers most of the filters [Fig. \ref{fig:agc_pgt}(b)].
In some layers however, the performance of PGT is slightly weaker than the baseline. The
$2^\textit{nd}$ convolutional layer has more zeroed out filters in PGT [Fig.
\ref{fig:agc_pgt}(e)] than in the baseline [Fig. \ref{fig:agc_pgt}(d)]. Despite that,
PGT achieves a higher overall accuracy (table \ref{tab:wobn_table}). This necessitates
the simultaneous use of AGC and PGT, for the non-BN ResNet-18.

@@

We provide performance metrics on the test set of ImageNet-1K for different batch sizes
for the non-BN ResNet-18 and also experiment with different methods (GC, AGC, PGT along
with their combinations). Table \ref{tab:wobn_table} shows the findings. To begin, we
use a batch size of 1024. The baseline performance for this batch size is drastically
inferior to baselines for other batch sizes. PGT helps regain some of the lost
performance by $0.682\%$ ($65.498\%$ vs. $64.816\%$). This illustrates that in
unnormalized networks, accuracy suffers significantly when batch sizes are large.
Additionally, the training process is often unstable at this batch size, resulting in
filters and sometimes entire layers frequently zeroing out (as seen in \ref{sec:Empi}).
At a batch size of 512, invoking PGT improves the training accuracy baseline by $1.48\%$
and the test accuracy baseline by $0.684\%$, while at a batch size of 256, the
improvement in training and test accuracies are $1.11\%$ and $1.018\%$ respectively. In
comparison, the test accuracy improvements obtained by GC and AGC at batch size of 256
is much less, at $0.27\%$ and $0.5\%$, respectively.

On the training accuracy front, since we get a significant boost ($1.48\%$ at batch size
of 512 and $1.11\%$ at batch size of 256), it leads us to infer that when PowerGrad
Transform is used, the network fits the training dataset more tightly and the
convergence optima is significantly superior. We also notice that the training versus
testing gap increases with PGT as compared to the gap at baseline even though both
training and test performance is improved. This allows us to infer that PGT increases
the generalization gap between the training and the test set, despite improvements in
both training and test performance. Therefore it allows us to conclude that the
improvements in training and test accuracies are obtained not through regularization
like it does in methods such as label smoothing; rather the improvements are obtained as
PGT enables the network to utilize its learning capacity better and arrive at a higher
performing optima at convergence, something which is inaccessible through traditional
gradient based training.

@@

As seen in Fig. \ref{fig:stats}(a), the logit norm increases as $\alpha$ falls from $1$
to $0$. In the initial training phase, PGT causes the gradient in both the valid and
wrong classes to rise as the network misclassifies majority of the examples. Due to the
exponential nature of the softmax function, the predicted probability distribution may
frequently be close to a delta distribution, even in instances of misclassifications.
PGT reshapes the predicted probability distribution. It redistributes probability from
the confident classes to the less confident ones. Gradient rises in all classes. We also
see that the final value of the loss rises as $\alpha$ drops, and that the logit norm
and the final value of the loss are linearly correlated Fig. \ref{fig:stats}(c). What is
surprising is that: \textit{greater accuracies may be acquired at larger loss values at
convergence}. This is markedly different from the coupled gradient descent based
training procedures. PGT enables the network to arrive at such optima where the loss
values are high, but both training and test perfomance is better. From these plots of
logits and losses we find that with the inclusion of PGT in the training process, the
model can have access to such regions of the loss landscape that is otherwise
inaccessible to traditional gradient based training procedures.

@@

\begin{table}[!t]
\centering
\caption{ Ablation study for ResNet-50 on ImageNet-1K. LS column denotes whether label
smoothing has been applied. A smoothing hyperparameter value of $0.1$ has been used. The
hyperparameter column that controls the amount of PGT gradient modification injected at
softmax, Eq. \ref{transformed_probabilities}. }
\label{tab:ablation_table}
\begin{tabular}{ccccccc}
\multirow{2}{*}{\textbf{Model}} & \multirow{2}{*}{\textbf{Scheduler}} & \textbf{Label} &
\textbf{PowerGrad} & \textbf{Train} & \textbf{Test} & \multirow{2}{*}{\textbf{Gap}} \\
& & \textbf{Smoothing} & \textbf{Transform ($\alpha$)} & \textbf{Accuracy (\%)} &
\textbf{Accuracy (\%)} & \\
\midrule
ResNet-50 & Step & \xmark & \xmark & 78.99 & 75.97 & 3.02 \\
& Step & \xmark & 0.3 & 79.56 & 76.494 & 3.066 \\
\cmidrule{2-7}
& Cosine & \xmark & \xmark & 79.18 & 76.56 & 2.62 \\
& Cosine & 0.1 & \xmark & 78.81 & 76.698 & 2.112 \\
\cmidrule{2-7}
& Cosine & \xmark & 0.3 & 79.43 & 76.886 & 2.544 \\
& Cosine & 0.1 & 0.3 & 78.47 & 76.968 & 1.502 \\
\cmidrule{2-7}
& Cosine & \xmark & 0.05 & 79.68 & 77.216 & 2.464 \\
& Cosine & 0.1 & 0.05 & 77.69 & 76.39 & 1.3 \\
\end{tabular}
\end{table}

We conduct an ablation study to investigate the effects of PowerGrad Transform for
different values of the hyperparameter ($\alpha$). Grid plots are made available in the
supplementary section. We have previously demonstrated from the experiments depicted in
section \ref{sec:Expe}, that PowerGrad Transform causes the network to arrive at a
better optima and fit the training dataset better than the baseline. In this ablation
study, we use the ResNet-50 architecture and we combine our proposed method with other
regularization techniques such as label smoothing and report our findings in table
\ref{tab:ablation_table}. We also investigate the two optimal peaks of the
hyperparameter ($\alpha$) obtained from ResNet-50's grid search ($\alpha=0.05$ and
$\alpha=0.3$). First, we examine the effect of PGT on the step scheduler baseline in
order to later compare it to the cosine scheduler baseline. PGT improves upon the step
scheduler baseline (test set) by a substantial margin with $0.524\%$ ($76.494\%$ as
opposed to $75.97\%$). Introducing the cosine scheduler yields a $0.59\%$ improvement
($76.56\%$ vs. $75.97\%$) over the step scheduler. After introducing label smoothing,
the test accuracy relative to the cosine scheduler baseline increases by only $0.138\%$
(from $76.56\%$ to $76.698\%$). However, introducing PGT with $\alpha=0.3$ alone
(without label smoothing) improves the cosine scheduler baseline by $0.326\%$
($76.886\%$ vs. $76.56\%$). Combining PGT ($\alpha=0.3$) with label smoothing improves
the performance on the test set further by $0.408\%$ (from $76.56\%$ to $76.968\%$) and
reduces the generalization gap (from $2.54\%$ to $1.5\%$). However, the impact of
combining PGT with label smoothing can vary depending on the value of the hyperparameter
$\alpha$. With a PGT hyperparameter value of $\alpha=0.05$, we notice the greatest
performance improvement, $1.246\%$ over the step scheduler test baseline and $0.656\%$
over the cosine scheduler test baseline. Adding label smoothing to PGT ($\alpha=0.05$)
hurts performance even though it reduces the generalization gap.

@@

>>>>

% \usepackage{xcolor} \usepackage{pagecolor} \pagecolor{black} \color{white}

@@

\begin{figure}[!t]
\centering
\begin{subfigure}{.33\textwidth}
\centering
\includegraphics[width=0.98\textwidth]{acc_vs_epoch_r18}
\caption{Plot of training and test accuracies (ResNet-18)}
\end{subfigure}%
\begin{subfigure}{.33\textwidth}
\centering
\includegraphics[width=0.98\textwidth]{acc_vs_epoch_r50}
\caption{Plot of training and test accuracies (ResNet-50)}
\end{subfigure}%
\begin{subfigure}{.33\textwidth}
\centering
\includegraphics[width=0.98\textwidth]{acc_vs_epoch_r50_60epochs}
\caption{Plot of test accuracies (ResNet-50)}
\end{subfigure}
\caption{ Log-linear plots of training and test accuracies and comparison with baseline
of batch-normalized variants: \textbf{(a)} ResNet-18 ($\alpha=0.25$), \textbf{(b)}
ResNet-50 ($\alpha=0.3$). For better visualization of accuracies obtained in the final
iterations, we plot both axes in log scale. PowerGrad Transform improves upon the
baseline in all cases. The corresponding accuracies are mentioned in Table
\ref{tab:imagenet_table}. \textbf{(c)} Training speed comparison between PGT ($60$
epochs) and baseline ($100$ epochs). They both converge to the same test accuracy
($76.5\%$) on ImageNet-1K. PGT's accelerated training saves $40\%$ of the epoch budget.
}
\label{fig:metrics}
\end{figure}

@@

We perform experiments on different variants ResNets using the ImageNet-1K dataset
\cite{deng2009imagenet}. All models are trained on four V100 GPUs with a batch size of
$1024$. We utilize a common set of hyperparameters for all experiments, which are as
follows: 100 epoch budget, 5 epochs linear warmup phase beginning with a learning rate
of $4\times 10^{-4}$ and ending with a peak learning rate of $0.4$, a momentum of $0.9$
and weight decay of $5\times 10^{-4}$, the SGD Nesterov optimizer and mixed precision.
In our studies, we employ either a step scheduler (dividing the learning rate by $10$ at
the $30^{th}$, $60^{th}$, and $90^{th}$ epochs) or a cosine decay scheduler
\cite{loshchilov2016sgdr}. We find $\alpha=0.25$ and $\alpha=0.05$ to be good choices
for ResNet-18 and ResNet-50, though larger values such as $\alpha=0.3$ also have good
performance as well. The experimental results are shown in Table
\ref{tab:imagenet_table}, and we mention the value of the PGT hyperparmeter ($\alpha$)
in each experiment. We explore different values of $\alpha$ in section \ref{sec:Abla}
and provide detailed grid plots in the supplementary section.

In our experiments with Squeeze-and-Excitation variant of ResNet-50 i.e.
SE-ResNet-50\cite{hu2018squeeze}, we observe significant improvements; a $0.97\%$ boost
in training accuracy and a $0.734\%$ increase in test accuracy. In our experiments with
ResNet-50, we find an increase of $0.5\%$ and $0.656\%$ performance enhancement over the
cosine scheduler baseline for training and testing respectively. The corresponding
improvement over the step scheduler baseline for ResNet-50 is $0.57\%$ (training) and
$0.524\%$ (testing). ResNet-101 sees a higher improvement in training fit, $0.81\%$ to
be exact, while the improvement over the test set is $0.362\%$. Smaller networks such as
SE-ResNet-18 and ResNet-18 sees accuracy boosts which are smaller but nevertheless
positive. Therefore we conclude that with PGT, the consistent improvements in training
accuracies across all cases is because the networks train better and arrive at better
optimas during convergence. Per epoch training and test accuracy plots of ResNet-18 and
ResNet-50 (both with and without PGT) are shown in Fig. \ref{fig:metrics}(a, b). For
better visualization of the top end of the plots, we scale both axes in log scale.
Because both training and test accuracies improve, it indicates that PowerGrad Transform
allows the network to learn better representations\footnote{Reproducible code, training
recipes for the experiments, pretrained checkpoints and training logs are provided at:
\\
\url{ https://github.com/bishshoy/power-grad-transform }. Code is adapted from
\cite{rw2019timm}.}.

These improvements are obtained with the number of epochs being kept the same as that of
the baseline model. Alternatively, practitioners can apply PGT and have the networks
converge to accuracy levels comparable to the baseline with a significantly reduced
epoch budget. In Fig. \ref{fig:metrics}(c), we illustrate one such instance in which we
train a ResNet-50 to its cosine scheduler baseline in just $60$ epochs with PGT, and
match its baseline performance that is acquired in $100$ epochs. This hints to the
observation that PGT not only makes the network perform better but also speeds up
training. Because of the acceleration in training that is made possible by PGT, the
total amount of training time can be decreased by $40\%$.

@@

AGC is excellent at eliminating the issue of filter and feature zeroing out. However,
AGC recovers a lower performance benefit than PGT. In the instance of PGT, we see that
it also mitigates the zeroing out phenomenon in most layers. In Fig.
\ref{fig:agc_pgt}(a), we see a plot of the $15^\textit{th}$ layer of the non-BN
ResNet-18 trained without PGT. As we can see that there has been quite a few filter
dropouts in the baseline. PGT recovers most of the filters [Fig. \ref{fig:agc_pgt}(b)].
In some layers however, the performance of PGT is slightly weaker than the baseline. The
$2^\textit{nd}$ convolutional layer has more zeroed out filters in PGT [Fig.
\ref{fig:agc_pgt}(e)] than in the baseline [Fig. \ref{fig:agc_pgt}(d)]. Despite that,
PGT achieves a higher overall accuracy (Table \ref{tab:wobn_table}). This necessitates
the simultaneous use of AGC and PGT, for the non-BN ResNet-18.

@@

We provide performance metrics on the test set of ImageNet-1K for different batch sizes
for the non-BN ResNet-18 and also experiment with different methods (GC, AGC, PGT along
with their combinations). Table \ref{tab:wobn_table} shows the findings. To begin, we
use a batch size of 1024. The baseline performance for this batch size is drastically
inferior to baselines for other batch sizes. PGT helps regain some of the lost
performance by $0.682\%$ ($65.498\%$ vs. $64.816\%$). This illustrates that in
unnormalized networks, accuracy suffers significantly when batch sizes are large.
Additionally, the training process is often unstable at this batch size, resulting in
filters and sometimes entire layers frequently zeroing out (as seen in section
\ref{sec:Empi}). At a batch size of 512, invoking PGT improves the training accuracy
baseline by $1.48\%$ and the test accuracy baseline by $0.684\%$, while at a batch size
of 256, the improvement in training and test accuracies are $1.11\%$ and $1.018\%$
respectively. In comparison, the test accuracy improvements obtained by GC and AGC at
batch size of 256 is much less, at $0.27\%$ and $0.5\%$, respectively.

On the training accuracy front, since we get a significant boost ($1.48\%$ at batch size
of 512 and $1.11\%$ at batch size of 256), it leads us to infer that when PowerGrad
Transform is used, the network fits the training dataset more tightly and the
convergence optima is significantly superior. We also notice that the training versus
testing gap increases with PGT as compared to the gap at baseline even though both
training and test accuracies improve. Therefore it allows us to conclude that the
improvements in training and test accuracies are obtained not through regularization
like it does in methods such as label smoothing; rather the improvements are obtained as
PGT enables the network to utilize its learning capacity better and arrive at a higher
performing optima at convergence, something which is inaccessible through traditional
gradient based training.

@@

As seen in Fig. \ref{fig:stats}(a), the logit norm increases as $\alpha$ falls from $1$
to $0$. In the initial training phase, PGT causes the gradient in both the valid and
wrong classes to rise as the network misclassifies majority of the examples. Due to the
exponential nature of the softmax function, the predicted probability distribution may
frequently be close to a delta distribution, even in instances of misclassifications.
PGT reshapes the predicted probability distribution. It redistributes probability from
the confident classes to the less confident ones. Gradient rises in all classes. We also
see that the final value of the loss rises as $\alpha$ drops, and that the logit norm
and the final value of the loss are linearly correlated Fig. \ref{fig:stats}(c). What is
surprising is that: \textit{it is possible to achieve higher accuracies even though the
loss values are larger during convergence}. In our studies with ResNet-50, for instance,
if PGT is not invoked, the corresponding test accuracy is $76.56\%$ (Table
\ref{tab:imagenet_table}) with a cross-entropy loss value of $0.852$. However, if PGT is
activated with $\alpha=0.05$, the corresponding test accuracy is $77.216\%$ (Table
\ref{tab:imagenet_table}) with a loss value of $2.360$. This is markedly different from
the coupled gradient descent based training procedures. PGT enables the network to
arrive at such optima where the loss values are high, but both training and test
perfomance is better. From these plots of logits and losses we find that with the
inclusion of PGT in the training process, the model can have access to such regions of
the loss landscape that is otherwise inaccessible to traditional gradient based training
procedures.

@@

\begin{table}[!t]
\centering
\caption{ Ablation study for ResNet-50 on ImageNet-1K. LS column denotes whether label
smoothing has been applied. A smoothing hyperparameter value of $0.1$ has been used. The
hyperparameter column that controls the amount of PGT gradient modification injected at
softmax, Eq. \ref{transformed_probabilities}. }
\label{tab:ablation_table}
\begin{tabular}{cccccccc}
\multirow{2}{*}{\textbf{\#Row}} & \multirow{2}{*}{\textbf{Model}} &
\multirow{2}{*}{\textbf{Scheduler}} & \textbf{Label} & \textbf{PowerGrad} &
\textbf{Train} & \textbf{Test} & \multirow{2}{*}{\textbf{Gap (\%)}} \\
& & & \textbf{Smoothing} & \textbf{Transform ($\alpha$)} & \textbf{Accuracy (\%)} &
\textbf{Accuracy (\%)} & \\
\midrule
1. & ResNet-50 & Step & \xmark & \xmark & 78.99 & 75.97 & 3.02 \\
2. & ResNet-50 & Step & \xmark & 0.3 & 79.56 & 76.494 & 3.066 \\
\cmidrule{2-8}
3. & ResNet-50 & Cosine & \xmark & \xmark & 79.18 & 76.56 & 2.62 \\
4. & ResNet-50 & Cosine & 0.1 & \xmark & 78.81 & 76.698 & 2.112 \\
\cmidrule{2-8}
5. & ResNet-50 & Cosine & \xmark & 0.3 & 79.43 & 76.886 & 2.544 \\
6. & ResNet-50 & Cosine & 0.1 & 0.3 & 78.47 & 76.968 & 1.502 \\
\cmidrule{2-8}
7. & ResNet-50 & Cosine & \xmark & 0.05 & 79.68 & 77.216 & 2.464 \\
8. & ResNet-50 & Cosine & 0.1 & 0.05 & 77.69 & 76.39 & 1.3 \\
\end{tabular}
\end{table}

We conduct an ablation study to investigate the effects of PowerGrad Transform for
different values of the hyperparameter ($\alpha$). Grid plots are made available in the
supplementary section. We have previously demonstrated from the experiments depicted in
section \ref{sec:Expe}, that PowerGrad Transform causes the network to arrive at a
better optima and fit the training dataset better than the baseline. In this ablation
study, we use the ResNet-50 architecture and we combine our proposed method with other
regularization techniques such as label smoothing and report our findings in Table
\ref{tab:ablation_table}. We also investigate the two optimal peaks of the
hyperparameter ($\alpha$) obtained from ResNet-50's grid search ($\alpha=0.05$ and
$\alpha=0.3$). First, we examine the effect of PGT on the step scheduler baseline in
order to later compare it to the cosine scheduler baseline. \textbf{Row-1)} We begin
with the step scheduler baseline ($75.97\%$). \textbf{Row-2)} PGT improves upon the step
scheduler baseline (test set) by a substantial margin with $0.524\%$ ($76.494\%$ as
opposed to $75.97\%$). \textbf{Row-3)} Introducing the cosine scheduler yields a
$0.59\%$ improvement ($76.56\%$ vs. $75.97\%$) over the step scheduler. \textbf{Row-4)}
After introducing label smoothing, the test accuracy relative to the cosine scheduler
baseline increases by only $0.138\%$ (from $76.56\%$ to $76.698\%$). \textbf{Row-5)}
However, introducing PGT with $\alpha=0.3$ alone (without label smoothing) improves the
cosine scheduler baseline by $0.326\%$ ($76.886\%$ vs. $76.56\%$). \textbf{Row-6)}
Combining PGT ($\alpha=0.3$) with label smoothing improves the performance on the test
set further by $0.408\%$ (from $76.56\%$ to $76.968\%$) and reduces the generalization
gap (from $2.54\%$ to $1.5\%$). However, the impact of combining PGT with label
smoothing can vary depending on the value of the hyperparameter ($\alpha$).
\textbf{Row-7)} With a PGT hyperparameter value of $\alpha=0.05$, we notice the greatest
performance improvement, $1.246\%$ over the step scheduler test baseline and $0.656\%$
over the cosine scheduler test baseline. \textbf{Row-8)} Adding label smoothing to PGT
($\alpha=0.05$) hurts performance even though it reduces the generalization gap.

@@

There is no effect of PGT on small datasets such as CIFAR-10. In these scenarios,
networks almost always achieve $100\%$ training accuracy, leaving no room for PGT to
assist.
